---
title:  "Meta-Analyzing ICC Estimates Graphs"
author: "Bethany"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float: yes
    toc_depth: 4
    code_folding: hide
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE}
rm(list = ls())
library(tidyverse)
library(kableExtra)
library(ggplot2)

load("data/ICC_sim_results_1.Rdata")
results1 <- results
load("data/ICC_sim_results_2.Rdata")
results2 <- results
load("data/ICC_sim_results_3.Rdata")
results3 <- results
load("data/ICC_sim_results_4.Rdata")
results4 <- results
load("data/ICC_sim_results_5.Rdata")
results5 <- results
load("data/ICC_sim_results_6.Rdata")
results6 <- results
load("data/ICC_sim_results_7.Rdata")
results7 <- results
load("data/ICC_sim_results_8.Rdata")
results8 <- results
load("data/ICC_sim_results_9.Rdata")
results9 <- results
load("data/ICC_sim_results_10.Rdata")
results10 <- results

results <- bind_rows(results1, results2, results3, results4, results5, results6, results7, results8, results9, results10)

source("3_performance_crit.R")


```


# Convergence

```{r}


test <- results |>  
  filter(sample_conv == "no") |>  
  filter(all_converge == TRUE)
#sum(is.na(results$pooled_icc_est))


results |>  filter(is.na(pooled_icc_est)) |>  
  group_by(nj_size) |>  
  tally() |> 
  knitr::kable() |>
  kableExtra::kable_styling() 


converge_sum <- results |>  
  group_by(method, var_icc_name, icc_est_n, nj_size, 
           n_bar_size, n_bar_prop, var_combo, tau)  |> 
  summarise(k = n(),
            num_no_converge = sum(is.na(pooled_icc_est)),
            num_converge = k - num_no_converge,
            num_converge2 = sum(!is.na(pooled_icc_est)),
            converge_rate = (num_converge/k)*100,
            nonconverge_rate = (num_no_converge/k)*100, 
            .groups = "drop"
            ) |>  
  ungroup()



#min(converge_sum$converge_rate)
#which(converge_sum$converge_rate < 100)


# number of samples that did not converge per method.
converge_sum |>
  group_by(method, var_icc_name) |>
  summarise(total_non_convergence = sum(num_no_converge, na.rm = TRUE),
            total_converged = sum(num_converge, na.rm= TRUE),
            converge_rate = (total_converged/(total_non_convergence + total_converged))*100, .groups = "drop" ) |>
  ungroup() |> 
  knitr::kable(digits = 3) |>
  kableExtra::kable_styling() 





```



Retain only 1000 samples per condition.

```{r}


results <- results |>  
  group_by(method, var_icc_name, icc_est_n, nj_size, n_bar_prop, n_bar_size, tau, var_combo)  |> 
  mutate(combination_id = cur_group_id()) |> 
  ungroup()



#results |>  group_by(combination_id) |>  tally()

#results |> filter(sample_conv != "no") |> filter(all_converge == TRUE) |>  group_by(combination_id) |>  tally()

results_all_converged <- results |>  
  filter(sample_conv != "no") |>  
  filter(all_converge == TRUE) |>  
  group_by(combination_id) |>  
  slice(1:1000) |> ungroup()


# calculate performance criteria
perf_crit <- calc_performance(results_all_converged)

perf_crit <- perf_crit |> 
  tidyr::unite("method2",  c( method, var_icc_name), remove = FALSE) |> 
  mutate(method2 = str_replace(method2, "_", "\n"))



perf_crit2 <- calc_performance_var(results_all_converged)




```



```{r}

perf_crit$var_combo_graph <- factor(perf_crit$var_combo,labels=c(
  'small_large' = 0.05,
  'medium_large' = 0.15,
  'large_large' = 0.25)) 

perf_crit <- perf_crit  |>  mutate(
  var_combo_graph = case_when(
    var_combo == 'small_large' ~ 0.05,
    var_combo == 'medium_large' ~ 0.15,
    var_combo == 'large_large' ~ 0.25,
  ),
  nj_size = case_when(
    nj_size == "small" ~'U[30, 50]',

    nj_size == "large" ~'U[50, 100]',
  ),
    n_bar_size = case_when(
    n_bar_size == "small" ~'U[10, 30]',

    n_bar_size == "large" ~'U[30, 50]',
  ),
  n_bar_graph = paste("n_bar_size = ", n_bar_size), 
  nj_graph = paste("nj_size = ", nj_size), 
  icc_est_n_graph = paste("k = ", icc_est_n)
) |>  
  separate(method2, into = c("model", "variance"), sep = "\n", remove = FALSE 
)  |>  
  mutate(variance = ifelse( variance == "Fisher TF", "Fisher\nTF", variance))


perf_crit$icc_est_n_graph <- factor(perf_crit$icc_est_n_graph,levels=c(
  "k =  20",
  "k =  50",
  "k =  100"))

```


# Pooled Estimate 

## Interactions

### True ICC vs num pooled ICCs
```{r}


perf_crit  |>  
  ggplot(aes(x = variance, y = rel_bias_icc, fill = model)) + 
  geom_hline(yintercept = .05, linetype = "dashed")  + 
  geom_hline(yintercept = -.05, linetype = "dashed")  + 
  geom_boxplot(alpha = .5) + 
  facet_grid( var_combo_graph ~ icc_est_n, 
             labeller = label_bquote(rows = rho ==.(var_combo_graph), 
                                            cols = k ==.(icc_est_n))) + 
  labs(x = NULL, y = "RPB", fill = NULL) + 
  theme_bw() +
  theme(
    legend.position = "bottom",
        axis.text.x = element_text(size = 6.5),
        axis.text.y = element_text(size = 6.5),

        plot.caption=element_text(hjust = 0, size = 6),
       # legend.title=element_text(size = 6), 
        legend.text=element_text(size = 6.5),
        axis.title.x = element_text(size=6.5),
        axis.title.y = element_text(size=6.5),
      #  strip.background =element_rect(fill="white")
        strip.text.x = element_text(size = 6.5, face="bold"),
        strip.text.y = element_text(size = 6.5, face="bold")
      )

ggsave("RPB_numICC.png", width = 6.8, height = 5, units = "in")






perf_crit  |>  
  ggplot(aes(x = variance, y = RMSE_rel_bias_icc, fill = model)) + 
  geom_hline(yintercept = .00, linetype = "dashed")  + 
  geom_boxplot(alpha = .5) + 
  facet_grid( var_combo_graph ~ icc_est_n, 
             labeller = label_bquote(rows = rho ==.(var_combo_graph), 
                                            cols = k ==.(icc_est_n))) + 
  labs(x = NULL, y = "RMSE", fill = NULL) + 
  theme_bw() +
  theme(
    legend.position = "bottom",
        axis.text.x = element_text(size = 6.5),
        axis.text.y = element_text(size = 6.5),

        plot.caption=element_text(hjust = 0, size = 6),
       # legend.title=element_text(size = 6), 
        legend.text=element_text(size = 6.5),
        axis.title.x = element_text(size=6.5),
        axis.title.y = element_text(size=6.5),
      #  strip.background =element_rect(fill="white")
        strip.text.x = element_text(size = 6.5, face="bold"),
        strip.text.y = element_text(size = 6.5, face="bold")
      )

ggsave("RMSE_numICC.png", width = 6.8, height = 5, units = "in")
```

### True ICC vs tau (between study heterogeneity)

```{r}



perf_crit  |> 
  ggplot(aes(x = variance, y = rel_bias_icc, fill = model)) + 
  geom_hline(yintercept = .05, linetype = "dashed")  + 
  geom_hline(yintercept = -.05, linetype = "dashed")  + 
  geom_boxplot(alpha = .5) + 
  facet_grid( var_combo_graph ~ tau, 
             labeller = label_bquote(rows = rho ==.(var_combo_graph), 
                                            cols = tau==.(tau))) + 
  labs(x = NULL, y = "RPB", fill = NULL) + 
  theme_bw() +
  theme(
    legend.position = "bottom",
        axis.text.x = element_text(size = 6.5),
        axis.text.y = element_text(size = 6.5),

        plot.caption=element_text(hjust = 0, size = 6),
       # legend.title=element_text(size = 6), 
        legend.text=element_text(size = 6.5),
        axis.title.x = element_text(size=6.5),
        axis.title.y = element_text(size=6.5),
      #  strip.background =element_rect(fill="white")
        strip.text.x = element_text(size = 6.5, face="bold"),
        strip.text.y = element_text(size = 6.5, face="bold")
      )

ggsave("RPB_tau.png", width = 6.8, height = 5, units = "in")



perf_crit  |> 
  ggplot(aes(x = variance, y = RMSE_rel_bias_icc, fill = model)) + 
  geom_hline(yintercept = .00, linetype = "dashed") + 
  geom_boxplot(alpha = .5) + 
  facet_grid( var_combo_graph ~ tau, 
             labeller = label_bquote(rows = rho ==.(var_combo_graph), 
                                            cols = tau==.(tau))) + 
  labs(x = NULL, y = "RMSE", fill = NULL) + 
  theme_bw() +
  theme(
    legend.position = "bottom",
        axis.text.x = element_text(size = 6.5),
        axis.text.y = element_text(size = 6.5),

        plot.caption=element_text(hjust = 0, size = 6),
       # legend.title=element_text(size = 6), 
        legend.text=element_text(size = 6.5),
        axis.title.x = element_text(size=6.5),
        axis.title.y = element_text(size=6.5),
      #  strip.background =element_rect(fill="white")
        strip.text.x = element_text(size = 6.5, face="bold"),
        strip.text.y = element_text(size = 6.5, face="bold")
      )
ggsave("RMSE_tau.png", width = 6.8, height = 5, units = "in")



```

### True ICC vs number of clusters

```{r}

perf_crit  |> 
  ggplot(aes(x = variance, y = rel_bias_icc, fill = model)) + 
  geom_hline(yintercept = .05, linetype = "dashed")  + 
  geom_hline(yintercept = -.05, linetype = "dashed")  + 
  geom_boxplot(alpha = .5) + 
  facet_grid( var_combo_graph ~ nj_size, 
             labeller = label_bquote(rows = rho ==.(var_combo_graph), 
                                            cols = j== .(nj_size))) + 
  labs(x = NULL, y = "RPB", fill = NULL) + 
  theme_bw() +
  theme(
    legend.position = "bottom",
        axis.text.x = element_text(size = 6.5),
        axis.text.y = element_text(size = 6.5),

        plot.caption=element_text(hjust = 0, size = 6),
       # legend.title=element_text(size = 6), 
        legend.text=element_text(size = 6.5),
        axis.title.x = element_text(size=6.5),
        axis.title.y = element_text(size=6.5),
      #  strip.background =element_rect(fill="white")
        strip.text.x = element_text(size = 6.5, face="bold"),
        strip.text.y = element_text(size = 6.5, face="bold")
      )

#ggsave("RPB_j.png", width = 6.8, height = 5, units = "in")



perf_crit  |> 
  ggplot(aes(x = variance, y = RMSE_rel_bias_icc, fill = model)) + 
  geom_hline(yintercept = .00, linetype = "dashed")  + 
  geom_boxplot(alpha = .5) + 
  facet_grid( var_combo_graph ~ nj_size, 
             labeller = label_bquote(rows = rho ==.(var_combo_graph), 
                                            cols = j== .(nj_size))) + 
  labs(x = NULL, y = "RMSE", fill = NULL) + 
  theme_bw() +
  theme(
    legend.position = "bottom",
        axis.text.x = element_text(size = 6.5),
        axis.text.y = element_text(size = 6.5),

        plot.caption=element_text(hjust = 0, size = 6),
       # legend.title=element_text(size = 6), 
        legend.text=element_text(size = 6.5),
        axis.title.x = element_text(size=6.5),
        axis.title.y = element_text(size=6.5),
      #  strip.background =element_rect(fill="white")
        strip.text.x = element_text(size = 6.5, face="bold"),
        strip.text.y = element_text(size = 6.5, face="bold")
      )
#ggsave("RMSE_j.png", width = 6.8, height = 5, units = "in")



```

### True ICC vs cluster size

```{r}



perf_crit  |> 
  ggplot(aes(x = variance, y = rel_bias_icc, fill = model)) + 
  geom_hline(yintercept = .05, linetype = "dashed")  + 
  geom_hline(yintercept = -.05, linetype = "dashed")  + 
  geom_boxplot(alpha = .5) + 
  facet_grid( var_combo_graph ~ n_bar_size, 
             labeller = label_bquote(rows = rho ==.(var_combo_graph), 
                                            cols = bar(n_j)==.(n_bar_size))) + 
  labs(x = NULL, y = "RPB", fill = NULL) + 
  theme_bw() +
  theme(
    legend.position = "bottom",
        axis.text.x = element_text(size = 6.5),
        axis.text.y = element_text(size = 6.5),

        plot.caption=element_text(hjust = 0, size = 6),
       # legend.title=element_text(size = 6), 
        legend.text=element_text(size = 6.5),
        axis.title.x = element_text(size=6.5),
        axis.title.y = element_text(size=6.5),
      #  strip.background =element_rect(fill="white")
        strip.text.x = element_text(size = 6.5, face="bold"),
        strip.text.y = element_text(size = 6.5, face="bold")
      )

#ggsave("RPB_nj.png", width = 6.8, height = 5, units = "in")





perf_crit  |> 
  ggplot(aes(x = variance, y = RMSE_rel_bias_icc, fill = model)) + 
  geom_hline(yintercept = .00, linetype = "dashed")  + 
  geom_boxplot(alpha = .5) + 
  facet_grid( var_combo_graph ~ n_bar_size, 
             labeller = label_bquote(rows = rho ==.(var_combo_graph), 
                                            cols = bar(n_j)==.(n_bar_size))) + 
  labs(x = NULL, y = "RMSE", fill = NULL) + 
  theme_bw() +
  theme(
    legend.position = "bottom",
        axis.text.x = element_text(size = 6.5),
        axis.text.y = element_text(size = 6.5),

        plot.caption=element_text(hjust = 0, size = 6),
       # legend.title=element_text(size = 6), 
        legend.text=element_text(size = 6.5),
        axis.title.x = element_text(size=6.5),
        axis.title.y = element_text(size=6.5),
      #  strip.background =element_rect(fill="white")
        strip.text.x = element_text(size = 6.5, face="bold"),
        strip.text.y = element_text(size = 6.5, face="bold")
      )

#ggsave("RMSE_nj.png", width = 6.8, height = 5, units = "in")

 


```


### True ICC vs Degree of unbalance

```{r}



perf_crit  |> 
  ggplot(aes(x = variance, y = rel_bias_icc, fill = model)) + 
  geom_hline(yintercept = .05, linetype = "dashed")  + 
  geom_hline(yintercept = -.05, linetype = "dashed")  + 
  geom_boxplot(alpha = .5) + 
  facet_grid( var_combo_graph ~ n_bar_prop, 
             labeller = label_bquote(rows = rho ==.(var_combo_graph), 
                                            cols = zeta ==.(n_bar_prop))) + 
  labs(x = NULL, y = "RPB", fill = NULL) + 
  theme_bw() +
  theme(
    legend.position = "bottom",
        axis.text.x = element_text(size = 6.5),
        axis.text.y = element_text(size = 6.5),

        plot.caption=element_text(hjust = 0, size = 6),
       # legend.title=element_text(size = 6), 
        legend.text=element_text(size = 6.5),
        axis.title.x = element_text(size=6.5),
        axis.title.y = element_text(size=6.5),
      #  strip.background =element_rect(fill="white")
        strip.text.x = element_text(size = 6.5, face="bold"),
        strip.text.y = element_text(size = 6.5, face="bold")
      )

#ggsave("RPB_n_bar_prop.png", width = 6.8, height = 5, units = "in")





perf_crit  |> 
  ggplot(aes(x = variance, y = RMSE_rel_bias_icc, fill = model)) + 
  geom_hline(yintercept = .00, linetype = "dashed")  + 
  geom_boxplot(alpha = .5) + 
  facet_grid( var_combo_graph ~ n_bar_prop, 
             labeller = label_bquote(rows = rho ==.(var_combo_graph), 
                                            cols =zeta ==.(n_bar_prop))) + 
  labs(x = NULL, y = "RMSE", fill = NULL) + 
  theme_bw() +
  theme(
    legend.position = "bottom",
        axis.text.x = element_text(size = 6.5),
        axis.text.y = element_text(size = 6.5),

        plot.caption=element_text(hjust = 0, size = 6),
       # legend.title=element_text(size = 6), 
        legend.text=element_text(size = 6.5),
        axis.title.x = element_text(size=6.5),
        axis.title.y = element_text(size=6.5),
      #  strip.background =element_rect(fill="white")
        strip.text.x = element_text(size = 6.5, face="bold"),
        strip.text.y = element_text(size = 6.5, face="bold")
      )

#ggsave("RMSE_n_bar_prop.png", width = 6.8, height = 5, units = "in")

 


```


### number clusters vs cluster size

```{r}




perf_crit  |> 
  ggplot(aes(x = variance, y = rel_bias_icc, fill = model)) + 
  geom_hline(yintercept = .05, linetype = "dashed")  + 
  geom_hline(yintercept = -.05, linetype = "dashed")  + 
  geom_boxplot(alpha = .5) + 
  facet_grid( nj_size ~ n_bar_size, 
             labeller = label_bquote(rows = j ==.(nj_size), 
                                            cols = bar(n_j)==.(n_bar_size))) + 
  labs(x = NULL, y = "RPB", fill = NULL) + 
  theme_bw() +
  theme(
    legend.position = "bottom",
        axis.text.x = element_text(size = 6.5),
        axis.text.y = element_text(size = 6.5),

        plot.caption=element_text(hjust = 0, size = 6),
       # legend.title=element_text(size = 6), 
        legend.text=element_text(size = 6.5),
        axis.title.x = element_text(size=6.5),
        axis.title.y = element_text(size=6.5),
      #  strip.background =element_rect(fill="white")
        strip.text.x = element_text(size = 6.5, face="bold"),
        strip.text.y = element_text(size = 6.5, face="bold")
      )

#ggsave("RPB_j_nj.png", width = 6.8, height = 5, units = "in")



perf_crit  |> ggplot(aes(x = variance, y = RMSE_rel_bias_icc, fill = model)) + 
  geom_hline(yintercept = .00, linetype = "dashed")  + 
  geom_boxplot(alpha = .5) + 
  facet_grid( nj_size ~ n_bar_size, 
             labeller = label_bquote(rows = j ==.(nj_size), 
                                            cols = bar(n_j)==.(n_bar_size))) + 
  labs(x = NULL, y = "RMSE", fill = NULL) + 
  theme_bw() +
  theme(
    legend.position = "bottom",
        axis.text.x = element_text(size = 6.5),
        axis.text.y = element_text(size = 6.5),

        plot.caption=element_text(hjust = 0, size = 6),
       # legend.title=element_text(size = 6), 
        legend.text=element_text(size = 6.5),
        axis.title.x = element_text(size=6.5),
        axis.title.y = element_text(size=6.5),
      #  strip.background =element_rect(fill="white")
        strip.text.x = element_text(size = 6.5, face="bold"),
        strip.text.y = element_text(size = 6.5, face="bold")
      )

#ggsave("RMSE_j_nj.png", width = 6.8, height = 5, units = "in")

# 


```


# SE of ICC

## Interactions

### True ICC vs num pooled ICCs

```{r}

perf_crit  |> ggplot(aes(x = variance, y = rel_bias_se_ICC, fill = model)) + 
  geom_hline(yintercept = .05, linetype = "dashed")  + 
  geom_hline(yintercept = -.05, linetype = "dashed")  + 
  geom_boxplot(alpha = .5) + 
  facet_grid( var_combo_graph ~ icc_est_n, 
             labeller = label_bquote(rows = rho ==.(var_combo_graph), 
                                            cols = k ==.(icc_est_n))) + 
  labs(x = NULL, y = "RSEB", fill = NULL) + 
  theme_bw() +
  theme(
    legend.position = "bottom",
        axis.text.x = element_text(size = 6.5),
        axis.text.y = element_text(size = 6.5),

        plot.caption=element_text(hjust = 0, size = 6),
       # legend.title=element_text(size = 6), 
        legend.text=element_text(size = 6.5),
        axis.title.x = element_text(size=6.5),
        axis.title.y = element_text(size=6.5),
      #  strip.background =element_rect(fill="white")
        strip.text.x = element_text(size = 6.5, face="bold"),
        strip.text.y = element_text(size = 6.5, face="bold")
      )

ggsave("RPB_se_numICC.png", width = 6.8, height = 5, units = "in")



```


```{r}


perf_crit  |> ggplot(aes(x = variance, y = rel_bias_se_ICC, fill = model)) + 
  geom_hline(yintercept = .05, linetype = "dashed")  + 
  geom_hline(yintercept = -.05, linetype = "dashed")  + 
  geom_boxplot(alpha = .5) + 
  facet_grid( var_combo ~ icc_est_n#, 
             #labeller = label_bquote(rows = rho ==.(var_combo), 
            #                                cols = k ==.(icc_est_n))
             ) + 
  labs(x = NULL, y = "RSEB", fill = NULL) + 
  theme_bw() +
  theme(
    legend.position = "bottom",
        axis.text.x = element_text(size = 6.5),
        axis.text.y = element_text(size = 6.5),

        plot.caption=element_text(hjust = 0, size = 6),
       # legend.title=element_text(size = 6), 
        legend.text=element_text(size = 6.5),
        axis.title.x = element_text(size=6.5),
        axis.title.y = element_text(size=6.5),
      #  strip.background =element_rect(fill="white")
        strip.text.x = element_text(size = 6.5, face="bold"),
        strip.text.y = element_text(size = 6.5, face="bold")
      )

#ggsave("RPB_se_numICC.png", width = 6.8, height = 5, units = "in")

```





```{r}
perf_crit$tau2 <- as.factor(perf_crit$tau)

perf_crit  |> 
  ggplot(aes(x = variance, y = rel_bias_se_ICC, fill  = model)) + 
  geom_hline(yintercept = .05, linetype = "dashed")  + 
  geom_hline(yintercept = -.05, linetype = "dashed")  + 
  geom_boxplot(outlier.shape = NA,alpha = 0.5) + 
  geom_jitter(aes(color = model, shape = tau2, fill = NA),
              position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.8, seed = 345435), 
              size = .5, alpha = 0.6) +
 facet_grid( var_combo_graph ~ icc_est_n, 
             labeller = label_bquote(rows = rho ==.(var_combo_graph), 
                                            cols = k ==.(icc_est_n))) + 
  labs(x = NULL, y = "RSEB", fill = NULL) +
  scale_color_manual(values = c("#FF6347", "steelblue")) + # Custom colors for points
  scale_fill_manual(values = c("pink", "lightblue")) + # Custom colors for boxplots 
   scale_shape_manual(values = c(1, 3, 2)) +
  theme_bw() +
  theme(
    legend.position = "bottom",
        axis.text.x = element_text(size = 6.5),
        axis.text.y = element_text(size = 6.5),

        plot.caption=element_text(hjust = 0, size = 6),
       # legend.title=element_text(size = 6), 
        legend.text=element_text(size = 6.5),
        axis.title.x = element_text(size=6.5),
        axis.title.y = element_text(size=6.5),
      #  strip.background =element_rect(fill="white")
        strip.text.x = element_text(size = 6.5, face="bold"),
        strip.text.y = element_text(size = 6.5, face="bold")
      ) 


#ggsave("RPB_se_numICC_alt.png", width = 6.8, height = 5, units = "in")
```


```{r}
perf_crit |>
  ggplot(aes(x = as.character(variance), y = rel_bias_se_ICC, 
             color = model, 
             shape = as.character(tau)
             )
         ) +
  geom_point(alpha = .8, 
           #  position = position_jitter(height = .3), 
             size = 1)   + 
  geom_hline(yintercept = .05, linetype = "dashed")  + 
  geom_hline(yintercept = -.05, linetype = "dashed")  +
  facet_grid( var_combo_graph ~ icc_est_n, 
             labeller = label_bquote(rows = rho ==.(var_combo_graph), 
                                            cols = k ==.(icc_est_n))) + 
  labs(
    x = NULL, 
    y ="RSEB",
    color = "", shape = ""
  ) + 
  theme_bw() +
  theme(
    plot.caption=element_text(hjust = 0, size = 10),
    legend.position= "bottom",
    panel.spacing.x = unit(5, "mm"), 
    panel.spacing.y = unit(5, "mm"),
  )


#ggsave("RPB_se_numICC_alt2.png", width = 6.8, height = 5, units = "in")

```



### True ICC vs tau (between study )

```{r}







perf_crit  |> ggplot(aes(x = variance, y = rel_bias_se_ICC, fill = model)) + 
  geom_hline(yintercept = .05, linetype = "dashed")  + 
  geom_hline(yintercept = -.05, linetype = "dashed")  + 
  geom_boxplot(alpha = .5) + 
  facet_grid( var_combo_graph ~ tau, 
             labeller = label_bquote(rows = rho ==.(var_combo_graph), 
                                            cols = tau==.(tau))) + 
  labs(x = NULL, y = "RPB", fill = NULL) + 
  theme_bw() +
  theme(
    legend.position = "bottom",
        axis.text.x = element_text(size = 6.5),
        axis.text.y = element_text(size = 6.5),

        plot.caption=element_text(hjust = 0, size = 6),
       # legend.title=element_text(size = 6), 
        legend.text=element_text(size = 6.5),
        axis.title.x = element_text(size=6.5),
        axis.title.y = element_text(size=6.5),
      #  strip.background =element_rect(fill="white")
        strip.text.x = element_text(size = 6.5, face="bold"),
        strip.text.y = element_text(size = 6.5, face="bold")
      )

#ggsave("RPB_se_tau.png", width = 6.8, height = 5, units = "in")




```


### True ICC vs number of clusters

```{r}


perf_crit  |> ggplot(aes(x = variance, y = rel_bias_se_ICC, fill = model)) + 
  geom_hline(yintercept = .05, linetype = "dashed")  + 
  geom_hline(yintercept = -.05, linetype = "dashed")  + 
  geom_boxplot(alpha = .5) + 
  facet_grid( var_combo_graph ~ nj_size, 
             labeller = label_bquote(rows = rho ==.(var_combo_graph), 
                                            cols = j== .(nj_size))) + 
  labs(x = NULL, y = "RPB", fill = NULL) + 
  theme_bw() +
  theme(
    legend.position = "bottom",
        axis.text.x = element_text(size = 6.5),
        axis.text.y = element_text(size = 6.5),

        plot.caption=element_text(hjust = 0, size = 6),
       # legend.title=element_text(size = 6), 
        legend.text=element_text(size = 6.5),
        axis.title.x = element_text(size=6.5),
        axis.title.y = element_text(size=6.5),
      #  strip.background =element_rect(fill="white")
        strip.text.x = element_text(size = 6.5, face="bold"),
        strip.text.y = element_text(size = 6.5, face="bold")
      )

#ggsave("RPB_se_j.png", width = 6.8, height = 5, units = "in")



```


### True ICC vs cluster size

```{r}







perf_crit  |> ggplot(aes(x = variance, y = rel_bias_se_ICC, fill = model)) + 
  geom_hline(yintercept = .05, linetype = "dashed")  + 
  geom_hline(yintercept = -.05, linetype = "dashed")  + 
  geom_boxplot(alpha = .5) + 
  facet_grid( var_combo_graph ~ n_bar_size, 
             labeller = label_bquote(rows = rho ==.(var_combo_graph), 
                                            cols = bar(n_j)==.(n_bar_size))) + 
  labs(x = NULL, y = "RPB", fill = NULL) + 
  theme_bw() +
  theme(
    legend.position = "bottom",
        axis.text.x = element_text(size = 6.5),
        axis.text.y = element_text(size = 6.5),

        plot.caption=element_text(hjust = 0, size = 6),
       # legend.title=element_text(size = 6), 
        legend.text=element_text(size = 6.5),
        axis.title.x = element_text(size=6.5),
        axis.title.y = element_text(size=6.5),
      #  strip.background =element_rect(fill="white")
        strip.text.x = element_text(size = 6.5, face="bold"),
        strip.text.y = element_text(size = 6.5, face="bold")
      )

#ggsave("RPB_se_nj.png", width = 6.8, height = 5, units = "in")





```

### True ICC vs Degree of unbalance

```{r}



perf_crit  |> 
  ggplot(aes(x = variance, y = rel_bias_se_ICC, fill = model)) + 
  geom_hline(yintercept = .05, linetype = "dashed")  + 
  geom_hline(yintercept = -.05, linetype = "dashed")  + 
  geom_boxplot(alpha = .5) + 
  facet_grid( var_combo_graph ~ n_bar_prop, 
             labeller = label_bquote(rows = rho ==.(var_combo_graph), 
                                            cols = zeta ==.(n_bar_prop))) + 
  labs(x = NULL, y = "RPB", fill = NULL) + 
  theme_bw() +
  theme(
    legend.position = "bottom",
        axis.text.x = element_text(size = 6.5),
        axis.text.y = element_text(size = 6.5),

        plot.caption=element_text(hjust = 0, size = 6),
       # legend.title=element_text(size = 6), 
        legend.text=element_text(size = 6.5),
        axis.title.x = element_text(size=6.5),
        axis.title.y = element_text(size=6.5),
      #  strip.background =element_rect(fill="white")
        strip.text.x = element_text(size = 6.5, face="bold"),
        strip.text.y = element_text(size = 6.5, face="bold")
      )

#ggsave("RPB_n_bar_prop.png", width = 6.8, height = 5, units = "in")





```



### number clusters vs cluster size
```{r}







perf_crit  |> ggplot(aes(x = variance, y = rel_bias_se_ICC, fill = model)) + 
  geom_hline(yintercept = .05, linetype = "dashed")  + 
  geom_hline(yintercept = -.05, linetype = "dashed")  + 
  geom_boxplot(alpha = .5) + 
  facet_grid( nj_size ~ n_bar_size, 
             labeller = label_bquote(rows = j ==.(nj_size), 
                                            cols = bar(n_j)==.(n_bar_size))) + 
  labs(x = NULL, y = "RPB", fill = NULL) + 
  theme_bw() +
  theme(
    legend.position = "bottom",
        axis.text.x = element_text(size = 6.5),
        axis.text.y = element_text(size = 6.5),

        plot.caption=element_text(hjust = 0, size = 6),
       # legend.title=element_text(size = 6), 
        legend.text=element_text(size = 6.5),
        axis.title.x = element_text(size=6.5),
        axis.title.y = element_text(size=6.5),
      #  strip.background =element_rect(fill="white")
        strip.text.x = element_text(size = 6.5, face="bold"),
        strip.text.y = element_text(size = 6.5, face="bold")
      )

#ggsave("RPB_se_j_nj.png", width = 6.8, height = 5, units = "in")





```





# L2 Variance

```{r}



perf_crit2$var_combo_graph <- factor(perf_crit2$var_combo,labels=c(
  'small_large'=0.05,
  'medium_large'=0.15,
  'large_large'=0.25)) 



perf_crit2 <- perf_crit2 |> mutate(
  nj_size = case_when(
    nj_size == "small" ~'U[30, 50]',

    nj_size == "large" ~'U[50, 100]',
  ))
  


perf_crit2 <- perf_crit2 |> mutate(
  n_bar_size = case_when(
    n_bar_size == "small" ~'U[10, 30]',

    n_bar_size == "large" ~'U[30, 50]',
  ))
  


perf_crit2 <- perf_crit2 |> mutate(
                                 
                                  
                                  icc_est_n_graph = paste("k = ", icc_est_n)
                              
                                  )

perf_crit2$icc_est_n_graph <- factor(perf_crit2$icc_est_n_graph,levels=c(
  "20",
  "50",
  "100"))



```

## Main Effects

### L2 variance 
```{r}




perf_crit2  |> ggplot(aes(x = var_combo_graph, y = rel_bias_clus)) + 
  geom_hline(yintercept = .05, linetype = "dashed")  + 
  geom_hline(yintercept = -.05, linetype = "dashed")  + 
  geom_boxplot(alpha = .5) + 
 # facet_grid( rows = vars(var_combo_graph)
              #labeller = label_parsed
#              ) + 
  labs(x = "ICC Parameter", y = "RPB") + 
  theme_bw() +
  theme(legend.position = "none",
        axis.text.x = element_text(size = 6, face="bold"),
        plot.caption=element_text(hjust = 0, size = 8),
        legend.title=element_text(size = 8), 
        legend.text=element_text(size = 8),
        axis.title.x = element_text(size=8),
        axis.title.y = element_text(size=8),
        strip.background =element_rect(fill="white"))



```


### L2 variance by tau

```{r}



perf_crit2  |> ggplot(aes(x = var_combo_graph, y = rel_bias_clus)) + 
  geom_hline(yintercept = .05, linetype = "dashed")  + 
  geom_hline(yintercept = -.05, linetype = "dashed")  + 
#  geom_hline(yintercept = 0, linetype = "solid", colour = "red")  + 
  geom_boxplot(alpha = .5) + 
  facet_grid(cols = vars(tau )
             , 
             labeller = label_bquote(cols = tau ==.(tau))) + 
  labs(x = "ICC Parameter", y = "RPB") + 
  theme_bw() +
  theme(legend.position = "none",
        axis.text.x = element_text(size = 6.5),
        axis.text.y = element_text(size = 6.5),
      #  plot.caption=element_text(hjust = 0, size = 8),
      #  legend.title=element_text(size = 8), 
      #  legend.text=element_text(size = 8),
        axis.title.x = element_text(size=6.5),
        axis.title.y = element_text(size=6.5),
       strip.text.x = element_text(size = 6.5, face="bold"),
        strip.text.y = element_text(size = 6.5, face="bold")
      )

ggsave("RPB_L2_tau_mean.png", width = 6.8, height = 5, units = "in")






```


### L2 variance by clustersize

```{r}



perf_crit2  |> ggplot(aes(x = var_combo_graph, y = rel_bias_clus)) + 
  geom_hline(yintercept = .05, linetype = "dashed")  + 
  geom_hline(yintercept = -.05, linetype = "dashed")  + 
#  geom_hline(yintercept = 0, linetype = "solid", colour = "red")  + 
  geom_boxplot(alpha = .5) + 
  facet_grid(cols = vars(nj_size )
             , 
             labeller = label_bquote(cols = j ==.(nj_size))) + 
  labs(x = "ICC Parameter", y = "RPB") + 
  theme_bw() +
  theme(legend.position = "none",
        axis.text.x = element_text(size = 6.5),
        axis.text.y = element_text(size = 6.5),
      #  plot.caption=element_text(hjust = 0, size = 8),
      #  legend.title=element_text(size = 8), 
      #  legend.text=element_text(size = 8),
        axis.title.x = element_text(size=6.5),
        axis.title.y = element_text(size=6.5),
       strip.text.x = element_text(size = 6.5, face="bold"),
        strip.text.y = element_text(size = 6.5, face="bold")
      )

ggsave("RPB_L2_j_mean.png", width = 6.8, height = 5, units = "in")







```
